DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-06 Draft Ped Metrics Example.Rmd
defend against missing columns

```{r combine-rd-sw-sh, echo = TRUE}
# combine the sidewalk and shoulder and roads data
x <- st_as_sf(nc_sw_sh) %>% mutate(LENGTH = as.integer(LENGTH)) %>% filter(RD_LOG_ID == 49435 & LENGTH > 1000)
x$RD_LOG_ID <- 43809
comb <- st_intersection(select(ncdf, RD_LOG_ID_R = RD_LOG_ID, 
                                     SEGMENT_ID_R = SEGMENT_ID,
                                     FULL_NAME_R = FULL_NAME, 
                                     LENGTH_R = LENGTH,
                                     road_class, RUCODE), 
                             st_buffer(bind_rows(nc_sw_sh, x), 50, endCapStyle="FLAT")) %>% 
  filter(RD_LOG_ID == RD_LOG_ID_R) %>%
  distinct(RD_LOG_ID_R, SEGMENT_ID_R, RD_LOG_ID, SEGMENT_ID, SIDE_OF_RO, .keep_all = TRUE) %>%
  mutate(distance = as.integer(st_length(.)))
#distance is the length of the matched road segment and sidewalk or shoulder 
comb %>% st_set_geometry(., NULL) %>% 
  group_by(road_class, SIDE_OF_RO, TYPE) %>%
  summarize(s_miles = sum(distance)/5280,
            miles = format(round(as.numeric(sum(distance)/5280), 1), 
                           digits = 1, nsmall=1, big.mark=","),
            .groups = "drop")
```

@@

@@

>>>>

```{r combine-rd-sw-sh, echo = TRUE}
# combine the sidewalk and shoulder and roads data
x <- st_as_sf(nc_sw_sh) %>% mutate(LENGTH = as.integer(LENGTH)) %>% filter(RD_LOG_ID == 49435 & LENGTH > 1000)
x$RD_LOG_ID <- 43809
comb <- st_intersection(select(ncdf, RD_LOG_ID_R = RD_LOG_ID, 
                                     SEGMENT_ID_R = SEGMENT_ID,
                                     FULL_NAME_R = FULL_NAME, 
                                     LENGTH_R = LENGTH,
                                     road_class, RUCODE), 
                             st_buffer(bind_rows(nc_sw_sh, x), 50, endCapStyle="FLAT")) %>% 
  filter(RD_LOG_ID == RD_LOG_ID_R) %>%
  distinct(RD_LOG_ID_R, SEGMENT_ID_R, RD_LOG_ID, SEGMENT_ID, SIDE_OF_RO, .keep_all = TRUE) %>%
  mutate(distance = as.integer(st_length(.)))

#distance is the length of the matched road segment and sidewalk or shoulder 
#comb %>% st_set_geometry(., NULL) %>% 
#  group_by(road_class, SIDE_OF_RO, TYPE) %>%
#  summarize(s_miles = sum(distance)/5280,
#            miles = format(round(as.numeric(sum(distance)/5280), 1), 
#                           digits = 1, nsmall=1, big.mark=","),
#            .groups = "drop")
```

@@

For pedestrian generators, we identify an area that is within 1 mile of the facility and evaluate roads therein in the same manner as the defined county areas, like UGAs and LAMIRDS.

@@

```{r}
libraries <- community %>%
  filter(TYPE == "PUBLIC LIBRARY")
```

Kitsap County has `r nrow(libraries)`

### 2022-10-06 child_single_geo.Rmd
defend against missing columns

# comb will have repeating segments when there are sh/sw on both sides
this_comb <- st_intersection(select(this_roads, RD_LOG_ID_R = RD_LOG_ID, 
                                     FULL_NAME_R = FULL_NAME, 
                                     road_class, 
                                     SEGMENT_ID_R = SEGMENT_ID), 
                             st_buffer(bind_rows(this_sw_sh, x), 50, endCapStyle="FLAT")) %>% 
  filter(RD_LOG_ID == RD_LOG_ID_R) %>%
  distinct(RD_LOG_ID_R, SEGMENT_ID_R, RD_LOG_ID, SEGMENT_ID, SIDE_OF_RO, .keep_all = TRUE) %>%
  mutate(distance = st_length(.))

@@

```{r eval=has_both}
this_comb_stand <- this_comb %>% 
  st_set_geometry(., NULL) %>% 
  mutate(setting = ifelse(RUCODE == 1, "Rural", 
                          ifelse(RUCODE == 2, "Urban", "Unknown")),
         ped_type = sub("\\:.*", "", TYPE),
         nn = paste(sub("paved ","",tolower(ped_type)), tolower(SIDE_OF_RO),sep ="_")) %>%
  pivot_wider(id_cols = c(-RD_LOG_ID:-TYPE,-ped_type), 
              names_from = nn, 
              values_from = WIDTH,
              values_fn = mean) %>%
  left_join(road_standards)

@@

>>>>

# comb will have repeating segments when there are sh/sw on both sides
this_comb <- st_intersection(select(this_roads, RD_LOG_ID_R = RD_LOG_ID, 
                                     SEGMENT_ID_R = SEGMENT_ID,
                                     FULL_NAME_R = FULL_NAME, 
                                     LENGTH_R = LENGTH,
                                     road_class, RUCODE), 
                             st_buffer(bind_rows(this_sw_sh, x), 50, endCapStyle="FLAT")) %>% 
  filter(RD_LOG_ID == RD_LOG_ID_R) %>%
  distinct(RD_LOG_ID_R, SEGMENT_ID_R, RD_LOG_ID, SEGMENT_ID, SIDE_OF_RO, .keep_all = TRUE) %>%
  mutate(distance = st_length(.))

@@

```{r eval=has_both}
this_comb_stand <- this_comb %>% 
  st_set_geometry(., NULL) %>% 
  mutate(setting = ifelse(RUCODE == 1, "Rural", 
                          ifelse(RUCODE == 2, "Urban", "Unknown")),
         ped_type = sub("\\:.*", "", TYPE),
         nn = paste(sub("paved ","",tolower(ped_type)), tolower(SIDE_OF_RO),sep ="_")) %>%
  pivot_wider(id_cols = c(-RD_LOG_ID:-TYPE,-ped_type), 
              names_from = nn, 
              values_from = WIDTH,
              values_fn = mean) %>%
  left_join(road_standards) %>%
  rowwise() %>% # now make sure that have all the columns
  mutate(sidewalk_left = ifelse("sidewalk_left" %in% names(.), sidewalk_left, NA),
         sidewalk_right = ifelse("sidewalk_right" %in% names(.), sidewalk_right, NA),
         shoulder_left = ifelse("shoulder_left" %in% names(.), shoulder_left, NA),
         shoulder_right = ifelse("shoulder_right" %in% names(.), shoulder_right, NA)
         )

@@

The overall score for pedestrian facilities in {{current_geo}} is `r nice_comma(this_comb_total_score)`, `r getScoreInterpretation(this_comb_total_score)`.
